---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE, results = 'hide')
library(tidyverse)
library(ggthemes)

cel <- drop_na(read_csv("Elections CELL DATA.csv"))
view(cel)

cces <- drop_na(read_csv("Cces data.csv"))
view(cces)


```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Jehangeer

## Exercise 1

Here, I'm making density plot for congress 112, showing which party have high legislative effective score.
(Higher means more effective)



```{r exercise1,echo=FALSE, results='hide', fig.keep='last'}

cel %>%
      filter(congress == 112) %>% 
      ggplot(aes(x = les))+
      geom_density()


Party <- recode(cel$dem, '1' = "Democratic", '0' = "Republican")
cel <- add_column(cel, Party)

cel %>%
      filter(congress == 112) %>% 
      ggplot(aes(x = les,fill = Party))+
      geom_density()+
      labs(x = "Count", y = "Legislative Effective Score", 
           title = "LES Score of Congress Parties")+
      facet_wrap(~Party)
    

```

## Exercise 2

Here, I have created a bar plot of the members of congress 112.
(American or African)


```{r exercise2,echo=FALSE, results='hide', fig.keep='last'}

cel %>%
      filter(congress == 112) %>%
      select(congress, afam) %>%
      ggplot(aes(x = afam))+
      geom_bar()
      
      
People <- recode(cel$afam, '0' = "American", '1'= "African")
cel <- add_column(cel, People)

ggplot(cel, aes(x = People, fill = People))+
      geom_bar()+
      scale_fill_manual(values = c("black", "red"))+
      labs(x = "Identities", y = "Numbers of People's", title = "Member's in Congress")

```

## Exercise 3

Scatter plot of four student's grades with annotations


```{r exercise3,echo=FALSE, results='hide', fig.keep='last'}

Students <-  c("Jehangeer", "Palwisha", "Putk", "Pem")
Grades <- c(45, 69, 38, 82)
Classes <- c(15,20,11,25)

data <- tibble(Students, Grades, Classes)

data %>% 
      ggplot(aes(x = Classes, y = Grades, color = Students))+
      geom_point()+
      geom_text(aes(label = Students), nudge_y = -5)+
      labs(title = "Student's Grades")+
      guides(color = FALSE)


```

## Exercise 4

Here, I have created a ggthemes template data plot of data mtcars comparison btw horsepower and miles per gallon.


```{r exercise4,echo=FALSE, results='hide', fig.keep='last'}

mtcars

ggplot(mtcars, aes(x = mpg, y = hp))+
      geom_line()+
      theme_few()+
      labs(title = " Mtcars Horsepower vs Mpg(ggthemes)", x = "Miles per gallon", y = "Horsepower")
   


```
