---
title: "Week 02 Peer Review"
output: html_document
---



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv("Cces data.csv"))


```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

#### Jehangeer

## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE, results='hide', fig.keep='last'}

ggplot(cces, aes(x = ideo5))+
      geom_bar()

# recoding ideo5 variable into categorical variable

Ideology <- recode(cces$ideo5, '1'= "Very Liberal", '2'= "Liberal", '3'= "Moderate", '4'= "Conservative", '5'= "Very Conservative")
cces <- add_column(cces, Ideology)

ggplot(cces, aes(x = Ideology, fill = Ideology))+
      geom_bar()+
      labs(x = "Ideology", y = "Count", title = "Respondent Ideology")+
      guides(fill =  FALSE)

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE, results='hide', fig.keep='last'}

ggplot(cces, aes(x = pew_religimp))+
      geom_bar()
      
party2 <- recode(cces$pew_religimp, '1'= "very important", '2'= "somewhat important", '3'= "Not to important", '4'= "Not at all important")

cces <- add_column(cces, party2)

ggplot(cces, aes(x = party2, fill = Ideology))+
      geom_bar()+
      labs(x = "Importance of Religion", y = "Count", title = "Importance of Religion by Ideology")


```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your values will be slightly different):


```{r exercise3,echo=FALSE, results='hide', fig.keep='last'}

Semester <- seq(1:6)
Students <- rep("Amanda", 6)
Grades <- runif(6, 80, 100)

data1 <- tibble(Semester,Students, Grades)

ggplot(data1, aes(x = Semester, y = Grades))+
      geom_line()

Semester <- seq(1:6)
Students <- rep("Betty", 6)
Grades <- runif(6, 80, 100)

data2 <- tibble(Semester,Students, Grades)


Semester <- seq(1:6)
Students <- rep("Carol", 6)
Grades <- runif(6, 80, 100)

data3 <- tibble(Semester,Students, Grades)


all_data <- bind_rows(data1, data2, data3)
view(all_data)

ggplot(all_data, aes(x = Semester, y = Grades, group = Students, color = Students))+
      geom_line()+
      labs(title = "Student Grades by Semester")+
      facet_wrap(~Students)+
      guides(color = FALSE)

```
